Transformation of forecasts for evaluating predictive performance in an epidemiological context

### 2023-01-17 main.tex

Probabilistic forecasts \citep{heldProbabilisticForecastingInfectious2017} play an important role in decision-making in epidemiology and public health \citep{reichCollaborativeMultiyearMultimodel2019, funkShorttermForecastsInform2020, cramerEvaluationIndividualEnsemble2021, bracherShorttermForecastingCOVID192021, europeancovid-19forecasthubEuropeanCovid19Forecast2021, sherrattPredictivePerformanceMultimodel2022}, as well as other areas as diverse as economics \citep{timmermannForecastingMethodsFinance2018, elliottForecastingEconomicsFinance2016} or meteorology \citep{gneitingWeatherForecastingEnsemble2005, kukkonenReviewOperationalRegionalscale2012}. Epidemiological modelling in particular has received widespread attention during the COVID-19 pandemic. Evaluations of forecasts can provide feedback for researchers to improve their models and train ensembles. It moreover helps decision-makers distinguish good from bad predictions and choose forecasters (used here and elsewhere in this manuscript to mean anyone or anything that issues a forecast) and models that should inform future decisions.

Probabilistic forecasts are usually evaluated using so-called proper scoring rules \citep{gneitingStrictlyProperScoring2007}, which return a numerical score as a function of the forecast and the observed data. Proper scoring rules are constructed such that forecasters are incentivised to report their true belief about the future. Examples of proper scoring rules that have been used to assess epidemiological forecasts are the Continuous Ranked Probability Score~\citep[CRPS,][]{gneitingStrictlyProperScoring2007} or its discrete equivalent, the Ranked Probability Score~\citep[RPS,][]{funkAssessingPerformanceRealtime2019}, and the Weighted Interval Score \citep{bracherEvaluatingEpidemicForecasts2021}. 
The CRPS measures the distance of the predictive distribution to the observed data as 
\begin{linenomath*}
\begin{equation*}
    \text{CRPS}(F, y) = \int_{-\infty}^\infty \left( F(x) - 1(x \geq y) \right)^2 dx,
\end{equation*}    
\end{linenomath*}
where $y$ is the true observed value and $F$ the cumulative distribution function (CDF) of the predictive distribution. The CRPS can be understood as a generalisation of the absolute error to predictive distributions, and interpreted n the natural scale of the data. The WIS is an approximation of the CRPS for predictive distributions represented by a set of predictive quantiles and is currently used to assess forecasts in COVID-19 Forecast Hubs in the US \citep{cramerCOVID19ForecastHub2020, cramerEvaluationIndividualEnsemble2021}, Europe \citep{sherrattPredictivePerformanceMultimodel2022}, Germany and Poland \citep{bracherShorttermForecastingCOVID192021, bracherNationalSubnationalShortterm2021}, as well as the US Influenza Forecasting Hub \citep{CdcepiFlusightforecastdata2022}. The WIS is defined as 
\begin{linenomath*}
\begin{equation*}
    \text{WIS}(F, y) = \frac{1}{K} \times \sum_{k = 1}^{K} 2 \times \left[ \boldsymbol{1}(y \leq q_{\tau_k}) - \tau_k \right] \times ( q_{\tau_k} - y), 
\end{equation*}
\end{linenomath*}
where $q_{\tau}$ is the $\tau$ quantile of the forecast $F$, $y$ is the observed outcome, $K$ is the number of predictive quantiles provided and $\boldsymbol{1}$ is the indicator function. The WIS can be decomposed into three components, dispersion, overprediction, underprediction, which reflect the width of the forecast and whether it was centred above or below the observed value. We show an alternative definition based on central prediction intervals in Section \ref{sec:alternative-wis} which illustrates this decomposition more clearly.

@@

In many fields, it is common practice to forecast transformed quantities (see e.g. \cite{taylorEvaluatingVolatilityInterval1999} in finance, \cite{mayrLogLevelVAR2015} in macroeconomics, \cite{loweStochasticRainfallrunoffForecasting2014} in hydrology or \cite{fuglstadDoesNonstationarySpatial2015} in meteorology). While the goal of the transformations is usually to improve the accuracy of the predictions, they can also be used to enhance and complement the evaluation process. 
In this paper, we argue that the aforementioned issues with evaluating forecasts based on measures of absolute error can be addressed by transforming the forecasts and observations prior to scoring using some strictly monotonic transformation. Strictly monotonic transformations can shift the focus of the evaluation in a way that may be more appropriate for epidemiological forecasts, while preserving the propriety of the score. Many different transformations may be appropriate and useful, depending on the exact context, the desired focus of the evaluation, and specific aspects of the forecasts that forecast consumers care most about (see a broader discussion in Section \ref{sec:discussion}).

@@

The remainder of the article is structured as follows. In Sections \ref{sec:methods:relative}--\ref{sec:methods:vst} we provide some mathematical intuition on applying the log-transformation prior to evaluating the CRPS, highlighting the connections to relative error measures, the epidemic growth rate and variance stabilizing transformations.
%We first provide a mathematical intuition of the impact of the log-transformation and its interpretation as relative error (Section \ref{sec:methods:relative}, measure of the accuracy of a forecast of the growth rate (Section \ref{sec:methods:growthrate}) and it's effect as a variance-stabilising transformation that makes can make scores independent of the mean of the forecast target (Section \ref{sec:methods:vst}. 
We then discuss practical considerations for applying transformations in general and the log-transformation in particular (Section \ref{sec:methods:considerations}) and the effect of the log-transformation on forecast rankings (section \ref{sec:methods:rankings}. To analyse the real-world implications of the log-transformation we use forecasts submitted to the European COVID-19 Forecast Hub  \citep{europeancovid-19forecasthubEuropeanCovid19Forecast2021, sherrattPredictivePerformanceMultimodel2022}. Finally, we provide scoring recommendations, discuss alternative transformations that may be useful in different contexts, and suggest further research avenues (Section \ref{sec:discussion}).

@@

To strengthen our intuition on how transforming outcomes prior to applying the CRPS shifts the emphasis between targets with high and low expected outcomes, Figure \ref{fig:SIM-wis-state-size-mean} shows the expected CRPS of ideal forecasters under different mean-variance relationships and transformations. We consider a Poisson distribution where $\sigma^2 = \mu$, a negative binomial distribution with $\theta = 10$ and $\sigma^2 = \mu + 0.1\mu^2$, and a normal distribution with constant variance. We see that when applying the CRPS on the natural scale, the expected CRPS grows with the variance of the predictive distribution (which is equal to the data-generating distribution for the ideal forecaster). The expected CRPS is constant only for the distribution with constant variance, and grows in $\mu$ for the other two. When applying a log-transformation first, the expected CRPS is almost independent of $\mu$ for the negative binomial distribution and large $\mu$, while smaller targets have higher expected CRPS in case of the Poisson distribution and the normal distribution with constant variance. When applying a square-root-transformation before the CRPS, the expected CRPS is independent of the mean for the Poisson-distribution, but not for the other two. As can be seen in Figures \ref{fig:SIM-wis-state-size-mean} and \ref{fig:score-approx}, the approximations presented above work quite well for our simulated example.

@@

Small discrete observed values can pose an additional problem as it may be difficult to reliably evaluate relative errors. A related issues occurs when the predictive distribution has a large probability mass on zero (or on very small values), as this can translate into an excessively wide forecast in relative terms. This can be seen in Figure \ref{fig:HUB-model-comparison-baseline}, where the dispersion component of the WIS is inflated for scores obtained after applying the natural logarithm where forecasts contained zero in its prediction intervals.

@@

\begin{figure}[h!]
\centering
\includegraphics[width = 1\textwidth]{output/figures/illustration-effect-log-ranking-crps.png}
\caption{Illustration of the effect of the log-transformation of the ranking for a single forecast. Shown are CRPS (or WIS, respectively) values as a function of the observed value for two forecasters. Model A issues a geometric distribution with mean $\mu = 10$ and variance $\sigma^2 = \mu + \mu^2 = 110$), while Model B issues a Poisson distribution with mean and variance equal to 10. Zeroes in this illustrative example were handled by adding one before applying the natural logarithm.}
\label{fig:illustration-ranking}
\end{figure}

@@

The forecasts used for the purpose of this illustration are forecasts submitted between the 8th of March 2021 and the 5th of December 2022 for reported cases and deaths from COVID-19. See \cite{sherrattPredictivePerformanceMultimodel2022} for a more thorough description of the data. We filtered all forecasts submitted to the Hub to only include models which have submitted forecasts for both deaths and cases for 4 horizons in 32 locations on at least 46 forecast dates (see Figure \ref{fig:HUB-num-avail-models}). We removed all observations marked as data anomalies by the European Forecast Hub \citep{sherrattPredictivePerformanceMultimodel2022} as well as all remaining negative observed values. In addition, we filtered out erroneous forecasts defined by any of the conditions listed in Table \ref{tab:erroneous}. Those forecasts were removed in order to be better able to illustrate the effects of the log-transformation on scores and eliminating distortions caused by outlier forecasters. All predictive quantiles were truncated at 0. We applied the log-transformation after adding 1 to all predictions and observed values. Where not otherwise stated, we report results for a two-week-ahead forecast horizon.

@@

Across the dataset, the average number of observed cases and deaths varied considerably by location and target type (see Figure \ref{fig:HUB-mean-locations}A and B). On the natural scale, scores also varied considerably across targets (see Figure\ref{fig:HUB-mean-locations}D) and locations (see Figure\ref{fig:HUB-mean-locations}C). On the log scale, scores were more evenly distributed between targets (see Figure\ref{fig:HUB-mean-locations}D) and locations (see Figure\ref{fig:HUB-mean-locations}C). Both on the natural scale as well to a slightly lesser extent on the log scale, scores increased considerably with increasing forecast horizon (see Figure \ref{fig:HUB-mean-locations}E). This reflects the increasing difficulty of forecasts further into the future and, for the log scale, corresponds with our expectations from Section \ref{sec:methods:growthrate}.

@@

As argued in Section \ref{sec:methods:vst}, the mean-variance, or mean-CRPS, relationship determines which transformation can serve as a VST. To assess this empirically, we ran the regression

\begin{equation*}
    \log[\text{CRPS}(F, y)] = \alpha + \beta \times \log[\text{median}(F)], 
\end{equation*}
where the predictive distribution $F$ and the observation $y$ are on the natural scale. This is equivalent to
\begin{equation*}
    \text{CRPS}(F, y) = \exp(\alpha) \times \text{median}(F)^\beta, 
\end{equation*}
meaning that we estimate a polynomial relationship between the predictive median and achieved CRPS. Note that we are using predictive medians rather than means as only the former are available in the European COVID-19 Forecast Hub. We applied the regression to case and death forecasts, pooled across horizons and stratified for one through four-week-ahead forecasts. Results are provided in Table \ref{tab:HUB-regression}. It can be seen that the estimates of $\beta$ always take a value below 1.  As the CRPS scales with the standard deviation (see Section \ref{sec:methods:vst}), this can be interpreted as a slightly sub-quadratic mean-variance relationship. The logarithmic transformation should thus approximately stabilize the variance (and CRPS), possibly leading to somewhat higher scores for smaller forecast targets. The square-root transformation, on the other hand, can be expected to still lead to higher CRPS values for targets of higher orders of magnitude.

@@

To check this, we ran the regressions
\begin{equation*}
    \text{CRPS}(F_{\log}, \log y) = \alpha_{\log} + \beta_{\log} \cdot \log{(\text{median}(F))},
\end{equation*}
where $F_{\log}$ is the predictive distribution for $\log(y)$, and
\begin{equation*}
    \text{CRPS}(F_{\sqrt{\ }}, \sqrt{y}) = \alpha_{\sqrt{\ }} + \beta_{\sqrt{\ }} \cdot \sqrt{\text{median}(F)},
\end{equation*} 
where $F_{\sqrt{\ }}$ is the predictive distribution on the square-root scale. As can be seen from Table \ref{tab:HUB-regression}, the results indeed indicate small targets lead to larger average CRPS when using the log transform ($\beta_{\log} < 0$), while the opposite is true for the square-root transform ($\beta_{\sqrt{\ }} > 0$). The results of the three regressions are also displayed in Figure \ref{fig:HUB-regression}. In this empirical example, the log transformation helps (albeit not perfectly), to stabilise WIS values and achieves this better suited than the square-root transformation.

@@

Figure Figure \ref{fig:HUB-rank-order} shows the changes in the ranking between different forecasting models. Encouragingly for the European Forecast Hub, the Hub ensemble, which is the forecast the organisers suggest forecast consumers make use of, remains the top forecasts across scoring schemes. For cases, the ILM-EKF model and the Forecast Hub baseline model exhibit the largest change in relative skill scores. For the ILM-EKF model the relative proportion of the score that is due to overprediction is reduced when applying a log-transformation before scoring (see Figure \ref{fig:HUB-rank-order}E. Instances where the model has overshot are penalised less heavily on the log scale, leading to an overall better score. For the Forecast Hub baseline model, the fact that it often puts relevant probability mass on zero (see Figure \ref{fig:HUB-model-comparison-baseline}), leads to worse scores after applying log-transformation due to large dispersion penalties. For deaths, the baseline model seems to get similarly penalised for its in relative terms highly forecasts. The performance of other models changes as well, but patterns are less discernible on this aggregate level.

@@

Applying a log-transformation prior to the WIS means that forecasts are evaluated in terms of relative errors and errors on the exponential growth rate, rather than absolute errors. The most important strength of this approach is that the evaluation better accommodates the exponential nature of the epidemiological process and the types of errors forecasters who accurately model those processes are expected to make. The log-transformation also helps avoid issues with scores being strongly influenced by the order of magnitude of the forecast quantity, which can be an issue when evaluating forecasts on the natural scale. 
A potential downside is that forecast evaluation is unreliable in situations where observed values are zero or very small. Including very small values in prediction intervals (see e.g. Figure \ref{fig:HUB-model-comparison-baseline}) can lead to excessive dispersion values on the log scale. 
Similarly, locations with lower incidences may get disproportionate weight (i.e. high scores) when evaluating forecasts on the log scale. \cite{bracherEvaluatingEpidemicForecasts2021} argue that the large weight given to forecasts for locations with high incidences is a desirable property, as it reflects performance on the targets we should care about most. On the other hand, scoring forecasts on the log scale may be less influenced by outliers and better reflect consistent performance across time, space, and forecast targets. It also gives higher weight to another type of situation one may care about, namely one in which numbers start to rise from a previously low level. 
If one is interested in scoring a forecast of the multiplicative, rather than the exponential growth rate, it may be better to use a different transformation, e.g. dividing every forecast and corresponding observed value by the previously last observed value when the forecast was made.

The log-transformation is only one of many transformations that may be useful and appropriate in an epidemiological context. One obvious option is to apply a population standardization to obtain incidence forecasts e.g., per 100,000 population If one is interested in multiplicative, rather than exponential growth rates, one could convert forecasts into forecasts for the multiplicative growth rate by dividing numbers by the last observed value. We suggested using the natural logarithm as a variance-stabilising transformation (VST) or alternatively the square-root transformation in the case of a Poisson distributed variable. Other VST like the Box-Cox \citep{boxAnalysisTransformations1964} are conceivable as well. Another promising transformation would be to take differences between forecasts on the log scale, or alternatively to divide each forecast by the forecast of the previous week (and analogously for observations), in order to obtain forecasts for week-to-week growth rates. One could then also ask forecasters to provide estimates of the weekly relative change applied to the latest data and subsequent forecast points directly. This would be akin to evaluating the shape of the predicted trajectory against the shape of the observed trajectory \citep[for a different approach to evaluating the shape of a forecast, see][]{srivastavaShapebasedEvaluationEpidemic2022}. This, unfortunately, is not feasible for forecasts stored as predictive quantiles, as the growth rate of the $\alpha$-quantile may be different from the $\alpha$-quantile of the growth-rate, but may be an interesting approach if predictive samples are available. It is possible to go beyond choosing a single transformation by constructing composite scores as a weighted sum of scores based on different transformations. This would make it possible to create custom scores and allow forecast consumers to assign explicit weights to different qualities of the forecasts they might care about.

>>>>

Probabilistic forecasts \citep{heldProbabilisticForecastingInfectious2017} play an important role in decision-making in epidemiology and public health \citep{reichCollaborativeMultiyearMultimodel2019, funkShorttermForecastsInform2020, cramerEvaluationIndividualEnsemble2021, bracherShorttermForecastingCOVID192021, europeancovid-19forecasthubEuropeanCovid19Forecast2021, sherrattPredictivePerformanceMultimodel2022}, as well as other areas as diverse as economics \citep{timmermannForecastingMethodsFinance2018, elliottForecastingEconomicsFinance2016} or meteorology \citep{gneitingWeatherForecastingEnsemble2005, kukkonenReviewOperationalRegionalscale2012}. Epidemiological modelling in particular has received widespread attention during the COVID-19 pandemic. Evaluations of forecasts can provide feedback for researchers to improve their models and train ensembles. It moreover helps decision-makers distinguish good from bad predictions and choose forecasters and models and models that should inform future decisions.

Probabilistic forecasts are usually evaluated using so-called proper scoring rules \citep{gneitingStrictlyProperScoring2007}, which return a numerical score as a function of the forecast and the observed data. Proper scoring rules are constructed such that forecasters (anyone or anything that issues a forecast) are incentivised to report their true belief about the future. Examples of proper scoring rules that have been used to assess epidemiological forecasts are the Continuous Ranked Probability Score~\citep[CRPS,][]{gneitingStrictlyProperScoring2007} or its discrete equivalent, the Ranked Probability Score~\citep[RPS,][]{funkAssessingPerformanceRealtime2019}, and the Weighted Interval Score \citep{bracherEvaluatingEpidemicForecasts2021}. 
The CRPS measures the distance of the predictive distribution to the observed data as 
\begin{linenomath*}
\begin{equation*}
    \text{CRPS}(F, y) = \int_{-\infty}^\infty \left( F(x) - 1(x \geq y) \right)^2 dx,
\end{equation*}    
\end{linenomath*}
where $y$ is the true observed value and $F$ the cumulative distribution function (CDF) of the predictive distribution. The CRPS can be understood as a generalisation of the absolute error to predictive distributions, and interpreted n the natural scale of the data. The WIS is an approximation of the CRPS for predictive distributions represented by a set of predictive quantiles and is currently used to assess forecasts in COVID-19 Forecast Hubs in the US \citep{cramerCOVID19ForecastHub2020, cramerEvaluationIndividualEnsemble2021}, Europe \citep{sherrattPredictivePerformanceMultimodel2022}, Germany and Poland \citep{bracherShorttermForecastingCOVID192021, bracherNationalSubnationalShortterm2021}, as well as the US Influenza Forecasting Hub \citep{CdcepiFlusightforecastdata2022}. The WIS is defined as 
\begin{linenomath*}
\begin{equation*}
    \text{WIS}(F, y) = \frac{1}{K} \times \sum_{k = 1}^{K} 2 \times \left[ \boldsymbol{1}(y \leq q_{\tau_k}) - \tau_k \right] \times ( q_{\tau_k} - y), 
\end{equation*}
\end{linenomath*}
where $q_{\tau}$ is the $\tau$ quantile of the forecast $F$, $y$ is the observed outcome, $K$ is the number of predictive quantiles provided and $\boldsymbol{1}$ is the indicator function. The WIS can be decomposed into three components, dispersion, overprediction, underprediction, which reflect the width of the forecast and whether it was centred above or below the observed value. We show an alternative definition based on central prediction intervals in Section \ref{sec:alternative-wis} which illustrates this decomposition more clearly.

@@

In many fields, it is common practice to forecast transformed quantities (see e.g. \cite{taylorEvaluatingVolatilityInterval1999} in finance, \cite{mayrLogLevelVAR2015} in macroeconomics, \cite{loweStochasticRainfallrunoffForecasting2014} in hydrology or \cite{fuglstadDoesNonstationarySpatial2015} in meteorology). While the goal of the transformations is usually to improve the accuracy of the predictions, they can also be used to enhance and complement the evaluation process. 
In this paper, we argue that the aforementioned issues with evaluating forecasts based on measures of absolute error on the natural scale can be addressed by transforming the forecasts and observations prior to scoring using some strictly monotonic transformation. Strictly monotonic transformations can shift the focus of the evaluation in a way that may be more appropriate for epidemiological forecasts, while preserving the propriety of the score. Many different transformations may be appropriate and useful, depending on the exact context, the desired focus of the evaluation, and specific aspects of the forecasts that forecast consumers care most about (see a broader discussion in Section \ref{sec:discussion}).

@@

The remainder of the article is structured as follows. In Sections \ref{sec:methods:relative}--\ref{sec:methods:vst} we provide some mathematical intuition on applying the log-transformation prior to evaluating the CRPS, highlighting the connections to relative error measures, the epidemic growth rate and variance stabilizing transformations.
%We first provide a mathematical intuition of the impact of the log-transformation and its interpretation as relative error (Section \ref{sec:methods:relative}, measure of the accuracy of a forecast of the growth rate (Section \ref{sec:methods:growthrate}) and it's effect as a variance-stabilising transformation that makes can make scores independent of the mean of the forecast target (Section \ref{sec:methods:vst}. 
We then discuss practical considerations for applying transformations in general and the log-transformation in particular (Section \ref{sec:methods:considerations}) and the effect of the log-transformation on forecast rankings (section \ref{sec:methods:rankings}). To analyse the real-world implications of the log-transformation we use forecasts submitted to the European COVID-19 Forecast Hub  \citep{europeancovid-19forecasthubEuropeanCovid19Forecast2021, sherrattPredictivePerformanceMultimodel2022}. Finally, we provide scoring recommendations, discuss alternative transformations that may be useful in different contexts, and suggest further research avenues (Section \ref{sec:discussion}).

@@

To strengthen our intuition on how transforming outcomes prior to applying the CRPS shifts the emphasis between targets with high and low expected outcomes, Figure \ref{fig:SIM-wis-state-size-mean} shows the expected CRPS of ideal forecasters under different mean-variance relationships and transformations. We consider a Poisson distribution where $\sigma^2 = \mu$, a negative binomial distribution with size parameter $\theta = 10$ and thus $\sigma^2 = \mu + \mu^2/10$, and a normal distribution with constant variance. We see that when applying the CRPS on the natural scale, the expected CRPS grows with the variance of the predictive distribution (which is equal to the data-generating distribution for the ideal forecaster). The expected CRPS is constant only for the distribution with constant variance, and grows in $\mu$ for the other two. When applying a log-transformation first, the expected CRPS is almost independent of $\mu$ for the negative binomial distribution and large $\mu$, while smaller targets have higher expected CRPS in case of the Poisson distribution and the normal distribution with constant variance. When applying a square-root-transformation before the CRPS, the expected CRPS is independent of the mean for the Poisson-distribution, but not for the other two (with a positive relationship in the normal case and a negative one for the negative binomial). As can be seen in Figures \ref{fig:SIM-wis-state-size-mean} and \ref{fig:score-approx}, the approximations presented above work quite well for our simulated example.

@@

Small discrete observed values can pose an additional problem as it may be difficult to reliably evaluate relative errors. A related issue occurs when the predictive distribution has a large probability mass on zero (or on very small values), as this can translate into an excessively wide forecast in relative terms. This can be seen in Figure \ref{fig:HUB-model-comparison-baseline}, where the dispersion component of the WIS is inflated for scores obtained after applying the natural logarithm where forecasts contained zero in its prediction intervals.

@@

\begin{figure}[h!]
\centering
\includegraphics[width = 1\textwidth]{output/figures/illustration-effect-log-ranking-crps.png}
\caption{Illustration of the effect of the log-transformation of the ranking for a single forecast. Shown are CRPS (or WIS, respectively) values as a function of the observed value for two forecasters. Model A issues a geometric distribution (a negative binomial distribution with size parameter $\theta = 1$) with mean $\mu = 10$ and variance $\sigma^2 = \mu + \mu^2 = 110$), while Model B issues a Poisson distribution with mean and variance equal to 10. Zeroes in this illustrative example were handled by adding one before applying the natural logarithm.}
\label{fig:illustration-ranking}
\end{figure}

@@

The forecasts used for the purpose of this illustration are forecasts submitted between the 8th of March 2021 and the 5th of December 2022 for reported cases and deaths from COVID-19. See \cite{sherrattPredictivePerformanceMultimodel2022} for a more thorough description of the data. We filtered all forecasts submitted to the Hub to only include models which have submitted forecasts for both deaths and cases for 4 horizons in 32 locations on at least 46 forecast dates (see Figure \ref{fig:HUB-num-avail-models}). We removed all observations marked as data anomalies by the European Forecast Hub \citep{sherrattPredictivePerformanceMultimodel2022} as well as all remaining negative observed values. In addition, we filtered out erroneous forecasts defined by any of the conditions listed in Table \ref{tab:erroneous}. Those forecasts were removed in order to be better able to illustrate the effects of the log-transformation on scores and eliminating distortions caused by outlier forecasters. All predictive quantiles were truncated at 0. We applied the log-transformation after adding 1 to all predictions and observed values. The analysis was conducted in \texttt{R} \citep{R}, using the \texttt{scoringutils} package \citep{bosseEvaluatingForecastsScoringutils2022} for forecast evaluation. All code is available on GitHub 
(\url{https://github.com/epiforecasts/transformation-forecast-evaluation}). Where not otherwise stated, we report results for a two-week-ahead forecast horizon.

@@

Across the dataset, the average number of observed cases and deaths varied considerably by location and target type (see Figure \ref{fig:HUB-mean-locations}A and B). On the natural scale, scores also varied considerably across targets (see Figure\ref{fig:HUB-mean-locations}D) and locations (see Figure\ref{fig:HUB-mean-locations}C). On the log scale, scores were more evenly distributed between targets (see Figure\ref{fig:HUB-mean-locations}D) and locations (see Figure\ref{fig:HUB-mean-locations}C). Both on the natural scale as well on the log scale, scores increased considerably with increasing forecast horizon (see Figure \ref{fig:HUB-mean-locations}E). This reflects the increasing difficulty of forecasts further into the future and, for the log scale, corresponds with our expectations from Section \ref{sec:methods:growthrate}.

@@

As argued in Section \ref{sec:methods:vst}, the mean-variance, or mean-CRPS, relationship determines which transformation can serve as a VST. We can analyse this relationship empirically by running a regression that explains the CRPS as a function of the central estimate of the predictive distribution. We ran the regression

\begin{equation*}
    \log[\text{CRPS}(F, y)] = \alpha + \beta \times \log[\text{median}(F)], 
\end{equation*}
where the predictive distribution $F$ and the observation $y$ are on the natural scale. This is equivalent to
\begin{equation*}
    \text{CRPS}(F, y) = \exp(\alpha) \times \text{median}(F)^\beta, 
\end{equation*}
meaning that we estimate a polynomial relationship between the predictive median and achieved CRPS. Note that we are using predictive medians rather than means as only the former are available in the European COVID-19 Forecast Hub. As the CRPS of an ideal forecaster scales with the standard deviation (see Section \ref{sec:methods:vst}), a value of $\beta = 1$ would imply a quadratic median-variance relationship, whereas a value of $\beta > 1$ ($\beta < 1$) would imply that the variance grows faster (slower) than the median. We applied the regression to case and death forecasts, pooled across horizons and stratified for one through four-week-ahead forecasts. Results are provided in Table \ref{tab:HUB-regression}. It can be seen that the estimates of $\beta$ always take a value below 1, implying a slightly sub-quadratic mean-variance relationship. The logarithmic transformation should thus approximately stabilize the variance (and CRPS), possibly leading to somewhat higher scores for smaller forecast targets. The square-root transformation, on the other hand, can be expected to still lead to higher CRPS values for targets of higher orders of magnitude.

@@

To check the relationship after the transformation, we ran the regressions
\begin{equation*}
    \text{CRPS}(F_{\log}, \log y) = \alpha_{\log} + \beta_{\log} \cdot \log{(\text{median}(F))},
\end{equation*}
where $F_{\log}$ is the predictive distribution for $\log(y)$, and
\begin{equation*}
    \text{CRPS}(F_{\sqrt{\ }}, \sqrt{y}) = \alpha_{\sqrt{\ }} + \beta_{\sqrt{\ }} \cdot \sqrt{\text{median}(F)},
\end{equation*} 
where $F_{\sqrt{\ }}$ is the predictive distribution on the square-root scale. A value of $beta_{\log} = 0$ (or $\beta_{\sqrt{\ } = 0}$, respectively, would imply that scores are independent of the median prediction after the transformation. A value smaller (larger) than 0 would imply that smaller (larger) targets lead to higher scores. As can be seen from Table \ref{tab:HUB-regression}, the results indeed indicate that small targets lead to larger average CRPS when using the log transform ($\beta_{\log} < 0$), while the opposite is true for the square-root transform ($\beta_{\sqrt{\ }} > 0$). The results of the three regressions are also displayed in Figure \ref{fig:HUB-regression}. In this empirical example, the log transformation thus helps (albeit not perfectly), to stabilise WIS values, and it does so more successfully than the square-root transformation (with $\beta_{\log}$ closer to zero than $\beta_{\sqrt{\ }}$).

@@

Figure Figure \ref{fig:HUB-rank-order} shows the changes in the ranking between different forecasting models. Encouragingly for the European Forecast Hub, the Hub ensemble, which is the forecast the organisers suggest forecast consumers make use of, remains the top forecasts across scoring schemes. For cases, the ILM-EKF model and the Forecast Hub baseline model exhibit the largest change in relative skill scores. For the ILM-EKF model the relative proportion of the score that is due to overprediction is reduced when applying a log-transformation before scoring (see Figure \ref{fig:HUB-rank-order}E. Instances where the model has overshot are penalised less heavily on the log scale, leading to an overall better score. For the Forecast Hub baseline model, the fact that it often puts relevant probability mass on zero (see Figure \ref{fig:HUB-model-comparison-baseline}), leads to worse scores after applying log-transformation due to large dispersion penalties. For deaths, the baseline model seems to get similarly penalised for its in relative terms highly dispersed forecasts. The performance of other models changes as well, but patterns are less discernible on this aggregate level.

@@

Applying a log-transformation prior to the WIS means that forecasts are evaluated in terms of relative errors and errors on the exponential growth rate, rather than absolute errors. The most important strength of this approach is that the evaluation better accommodates the exponential nature of the epidemiological process and the types of errors forecasters who accurately model those processes are expected to make. The log-transformation also helps avoid issues with scores being strongly influenced by the order of magnitude of the forecast quantity, which can be an issue when evaluating forecasts on the natural scale. 
A potential downside is that forecast evaluation is unreliable in situations where observed values are zero or very small. Including very small values in prediction intervals (see e.g. Figure \ref{fig:HUB-model-comparison-baseline}) can lead to excessive dispersion values on the log scale. 
Similarly, locations with lower incidences may get disproportionate weight (i.e. high scores) when evaluating forecasts on the log scale. \cite{bracherEvaluatingEpidemicForecasts2021} argue that the large weight given to forecasts for locations with high incidences is a desirable property, as it reflects performance on the targets we should care about most. On the other hand, scoring forecasts on the log scale may be less influenced by outliers and better reflect consistent performance across time, space, and forecast targets. It also gives higher weight to another type of situation one may care about, namely one in which numbers start to rise from a previously low level.

The log-transformation is only one of many transformations that may be useful and appropriate in an epidemiological context. One obvious option is to apply a population standardization to obtain incidence forecasts e.g., per 100,000 population ( \citep{abbottEvaluatingEpidemiologicallyMotivated2022}. If one is interested in multiplicative, rather than exponential growth rates, one could convert forecasts into forecasts for the multiplicative growth rate by dividing numbers by the last observed value. We suggested using the natural logarithm as a variance-stabilising transformation (VST) or alternatively the square-root transformation in the case of a Poisson distributed variable. Other VST like the Box-Cox \citep{boxAnalysisTransformations1964} are conceivable as well. Another promising transformation would be to take differences between forecasts on the log scale, or alternatively to divide each forecast by the forecast of the previous week (and analogously for observations), in order to obtain forecasts for week-to-week growth rates. One could then also ask forecasters to provide estimates of the weekly relative change applied to the latest data and subsequent forecast points directly. This would be akin to evaluating the shape of the predicted trajectory against the shape of the observed trajectory \citep[for a different approach to evaluating the shape of a forecast, see][]{srivastavaShapebasedEvaluationEpidemic2022}. This, unfortunately, is not feasible for forecasts stored as predictive quantiles, as the growth rate of the $\alpha$-quantile may be different from the $\alpha$-quantile of the growth-rate, but may be an interesting approach if predictive samples are available. It is possible to go beyond choosing a single transformation by constructing composite scores as a weighted sum of scores based on different transformations. This would make it possible to create custom scores and allow forecast consumers to assign explicit weights to different qualities of the forecasts they might care about.
